---
title: "Cabbages"
author: "Eduardo Noriega"
date: "September 7, 2022"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  
$H_0$: There is no difference in vitamin C between C39 and C52 cultivation  
$H_A$: The average amount of Vitamin C is statistically different in C39 than the C52 cultivation

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

The response variable is how much vitamin C is numerical  
The explanatory numerical is which cultivation method, it is a categorical

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

### Numerical Descriptive Results


```{r}
plot(VitC~Cult,data=veggy)
```
  
  This box plot shows that the median of C52 cultivation has a higher content of vitamin C of versus the amount of vitamin C in C39 cultivation

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

This table shows that the median amount of vitamin C of C39 is 51, and the cultivation of C52 has 64.5 of vitamin C

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfies the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The t-test shows that the P value is 0.00000003405,and it is less than 0.05, so I reject the null hypothesis.


# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhaps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The P value was 0.00000003405, which means that there is a difference between cultivation C39 and C52. C52 has a mean of 64.4 of vitamin C, and C39 has a mean of 51.5 of vitamin C, which is lower than C52.
